|

### 2024-03-18 manuscript/manuscript.qmd
update

[!Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"}

@@

[!Longitudinal Models/Data Structures](img/Mindmap1copy.png){#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"}

>>>>

![Figure 3 Statistical modeling of brain imaging data](img/Picture1.png)

<!-- ![Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"} -->

<img src="img/StabilityChange.png" alt="Types of Stability and Change" width="50%" height="auto"/>

![Types of Stability and Change](img/StabilityChange.png){width=50%}

![Types of Stability and Change](img/StabilityChange.png){fig-width=50%}

![Types of Stability and Change](img/StabilityChange.png)

<!-- ![Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram."}

[!Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"} -->

@@

![Longitudinal Models/Data Structures](img/Mindmap1.png)

<!-- [![Longitudinal Models/Data Structures](img/Mindmap1copy.png)]{#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="100" height="100" fig-align="left"}  -->
